Reproducible Research: Peer Assessment 1
========================================================
This assignment makes use of data from a personal activity monitoring device. This device collects data at 5 mintue intervals throughout the day. The data consists of two monthes of data from an anonymous individual collected during the monthes of October and November, 2012 and include the number of steps taken in 5 minute intervals each day. This assignment shows the results detailed below.


### 1. load in data
```{r data}
    setwd("c:\\DataScience_Reproduce")
    data <- read.csv("activity.csv") 
```

### 2. display histogram of total number of steps taken everyday (ignor na) 
```{r figure1}
    step_sum <- aggregate(steps~date,data=data,sum)
    hist(step_sum$steps,main="Total number of steps taken per day",xlab="steps")
```

### 3. find mean and median of total number of steps taken per day
```{r}
    mean(step_sum$steps)
    median(step_sum$steps)
```

### 4. display a plot: average daily activity pattern 
```{r figure2}
    step_ave <- aggregate(steps~interval, data=data,mean)
    plot(step_ave$interval, step_ave$steps,type="l",xlab="5-minute interval",
         ylab="ave.number of steps", main="average daily activity pattern")
```

### 5. find the interval with maximun steps
``` {r max}
interval <- step_ave[which(step_ave$steps==max(step_ave$steps)),]
interval
```

### 6. report total number of NA
```{r find_NA} 
    sum(is.na(data))
```

### 7. Input missing value with mean of each interval, built new dataset
```{r fill_NA}
    new_data <- data
    index <- which(is.na(data))
    new_data[index,1] <- replace(new_data[index,1], 
                        new_data[index,3]==step_ave$interval,step_ave$steps) 
```

### 8. display histogram of total number of steps taken everyday from new dataset
```{r figure3}
    new_step_sum <- aggregate(steps~date,data=new_data,sum)
    hist(new_step_sum$steps,main="Total number of steps taken per day",
         xlab="steps")
    mean(new_step_sum$steps)
    median(new_step_sum$steps)
```
Comparing the orginal data(with na) and the new data(replace na by mean of corresponding 5-min interval), it shows the same mean and the Frequency of total steps are higher with the new data. The reason for both is because the missing value is replaced by the corresponding 5-min interval.

### 9. add a new column(day) in the new dataset and define it as 'weekday' or 'weekend' 
```{r check_day} 
    new_data$day <- weekdays(as.Date(new_data$date))
    new_data$day <- replace(new_data$day,new_data$day=="Saturday"|
                            new_data$day=="Sunday","weekend")
    new_data$day <- replace(new_data$day,new_data$day!="weekend","weekday")
```

### 10. display plots: average daily activity pattern for 'weekend' and 'weekday'
```{r figure4}
    weekend_data <- subset(new_data[,1:3],new_data$day=="weekend")
    weekday_data <- subset(new_data[,1:3],new_data$day=="weekday")
    weekend_ave <- aggregate(steps~interval,data=weekend_data,mean)
    weekday_ave <- aggregate(steps~interval,data=weekday_data,mean)

    par(mfrow=c(2,1))
    plot(weekend_ave$interval,weekend_ave$steps,type="l",xlab="5-min interval",
        ylab="ave.number of steps",main="weekend average daily activity pattern")
    plot(weekday_ave$interval,weekday_ave$steps,type="l",xlab="5-min interval",
        ylab="ave.number of steps",main="weekday average daily activity pattern")
```
It is observed that average daily activity pattern for 'weekend' and 'weekday' is different